Computer Science House Constitution

### 2024-04-25 constitution.tex
226 small wording changes (#226)
* I removed the two lines that are illegal

* I think I deleted Socials when I put the table together but also I'm blaming Ella

* Changed 6.A.2.A to reduce wording, changed wording in some section that allowed everyone to be removed from the org by appeal

---------

Co-authored-by: ikopke23 <144629825+ik6335@users.noreply.github.com>

\asubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay requested dues, they may appeal their situation to the Financial Director.
The Financial Director then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
If the Financial Director decides their situation warrants no action, the member may appeal this decision to E-Board.
If appealed, E-Board may provide an extension and/or reduction to the member.
If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
All dues must be collected in full before the annual Membership Eval, as defined in \ref{Membership Evaluation}.
After this date, dues collection is suspended until the start of the next academic year.
\asubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
	\begin{tabular}[c]{|l c|}
		\hline
		Directorship & Percentage of Dues
		\\ \hline
		\hline
		OpComm       & 20\%
		\\ \hline
		Social       & 20\%
		\\ \hline
		R\&D         & 20\%
		\\ \hline
		IMPs         & 15\%
		\\ \hline
		History      & 10\%
		\\ \hline
		Evals        & 5\%
		\\ \hline
		PR           & 5\%
		\\ \hline
		Accumulated  & 5\%
		\\ \hline
	\end{tabular}
\end{center}

@@

\asubsection{Appeals Process}
If a member disagrees with the outcome of any Eval and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
\\* \\*
If the member is still unsatisfied after being heard by E-Board, the appeal may be brought to the attention of the ResLife Advisor.

>>>>

\asubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
Members may appeal their situation to the Financial Director or E-board in the case that the member is dissatisfied with the Financial Director's decision.
The Financial Director, or E-board, then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
\\*\\*
If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
All dues must be collected in full before the annual Membership Eval, as defined in \ref{Membership Evaluation}.
After this date, dues collection is suspended until the start of the next academic year.
\asubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
	\begin{tabular}[c]{|l c|}
		\hline
		Directorship & Percentage of Dues
		\\ \hline
		\hline
		OpComm       & 20\%
		\\ \hline
		Social       & 20\%
		\\ \hline
		R\&D         & 20\%
		\\ \hline
		IMPs         & 15\%
		\\ \hline
		History      & 10\%
		\\ \hline
		Evals        & 5\%
		\\ \hline
		PR           & 5\%
		\\ \hline
		Accumulated  & 5\%
		\\ \hline
	\end{tabular}
\end{center}

@@

\asubsection{Appeals Process}
If a member disagrees with the outcome of any non-passing Eval and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
\\* \\*
If the member is still unsatisfied after being heard by E-Board, the appeal may be brought to the attention of the ResLife Advisor.
